Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
some intro blah

>>>>

A key goal in improving patient-clinician communication is
establishing a common context for communication with which a shared
understanding can be established.  This understanding is
bi-directional, in the sense that, both the patient needs to be able
to properly interpret what the clincian is trying to convey to him or
her, while the clinician needs to be able to arrive at an accurate
characterisation of the patient's situation, as updated since the last
time he or she met with the patient.

One of the most promising technologies to help provide a common
context of communication is the patient-centric electronic health
record\cite{ehr} which constitute a complete medical history of
a patient as recorded through his or her entire life. (...)

% challenges to 
% background on authors
%
